### 2020-12-09 paper/localpsf.tex
literature review gah

We build upon a class of product convolution approximations in which the functions, $\varphi_i$, are impulse responses of $\mathcal{A}$ to point sources at a collection of points $x_i$ [CITE BIG LIST]. 
%The primary question in methods of this type are how to choose the points $x_i$, and how to choose the weighting functions $w_i$.
A popular choice for methods in this class is to choose the points $x_i$ to be nodes in a regular grid, and interpolate the functions $\varphi_i$ with piecewise linear interpolation [CITE NAGY], or splines [CITE SPLINES]. Adaptive refinement of the grid was proposed in [CITE], and we demonstrated a practical algorithm for adaptive refinement in our previous work [CITE MY PAPER]. Even with adaptive refinement, the number of points $x_i$ may be large, and computing the functions $\varphi_i$ requires one matrix vector product with $\mathcal{A}$ for each point $x_i$, which is computationally costly. A key innovation in this paper is that we pick points $x_i$ in such a way that many $\varphi_i$ are computed with each matrix vector product. We do this by taking advantage of the fact that the functions $\varphi_i$ are locally supported; existing methods typically do not require this local support property.

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used as an estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. For example, if the width of $\varphi_p$ is one meter, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than one meter in size.
%in which the length scales of the functions $\varphi_x$ are estimated for all $x$ simultaneously by applying $\mathcal{A}^T$ to a small number of random noise functions, $\zeta$, and post-processing the results. 
In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method achieves substantially better estimates of the supports than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the previous resolution analysis method does not have this requirement.

@@

In astronomy image deblurring applications, the point source positions typically correspond to locations of stars in an image, which are fixed.

>>>>

We build upon the class of product convolution approximations in which the functions, $\varphi_i$, are impulse responses of $\mathcal{A}$ to point sources at a collection of points $x_i$ [CITE BIG LIST]. 
%The primary question in methods of this type are how to choose the points $x_i$, and how to choose the weighting functions $w_i$.
A popular choice for methods in this class is to choose the points $x_i$ to be nodes in a regular grid, and interpolate the functions $\varphi_i$ with piecewise linear interpolation [CITE NAGY], or splines [CITE SPLINES]. With a regular grid, a large number of points $x_i$ is typically required to achieve an accurate product-convolution approximation. This is computationally prohibitive in our applications, because computing the functions $\varphi_i$ requires one matrix vector product with $\mathcal{A}$ for each point $x_i$, and each of these matrix vector products is extremely computationally costly. One can reduce the computational cost by starting with a coarse grid of points $x_i$, then adaptively refining the grid only in the regions where the error in the approximation is large [CITE, CITE MY PAPER]. But even with adaptive refinement, the required number of matrix vector products with $\mathcal{A}$ can be large. The key innovation in this paper is that we pick points $x_i$ in such a way that many $\varphi_i$ are computed with each matrix vector product. We do this by taking advantage of the fact that the functions $\varphi_i$ are locally supported; existing methods typically do not require this local support property.

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used as an estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. For example, if the width of $\varphi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size.
%in which the length scales of the functions $\varphi_x$ are estimated for all $x$ simultaneously by applying $\mathcal{A}^T$ to a small number of random noise functions, $\zeta$, and post-processing the results. 
In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method estimates the support of $\varphi_p$ more accurately than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

%In astronomy image deblurring applications, the point source positions typically correspond to locations of stars in an image, which are fixed.
